% Sanjeev Singh Resume
% Based on Deedy Resume Template
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX


\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}
\usepackage{url}
\urlstyle{same}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sanjeev Singh}{ 
Senior Software Engineer - Full-Stack Developer\\
\href{mailto:sanjeev.singh0279@gmail.com}{sanjeev.singh0279@gmail.com} | \href{tel:6284207388}{628-420-7388} | \href{https://www.linkedin.com/in/sanjeevsingh27}{linkedin.com/in/sanjeevsingh27}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OBJECTIVE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Objective}
Software Engineer with 4+ years building user-centric web apps. Proficient in JavaScript, TypeScript, React, and modern frontend tech. Team player dedicated to creating scalable, high-performance solutions.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Adobe}
\descript{| Senior Software Engineer }
\location{June 2022 – Present | Noida, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built complete UI for \textbf{Text-to-Template} generative AI feature, a flagship product in Adobe Express, enabling users to create editable designs from prompts and images across desktop and mobile platforms; resolved critical memory leaks and performance issues during mobile optimization, implemented "Bring Your Own Image" functionality, and developed metering system for credit-based monetization.
\item Developed custom \textbf{UI component library} for Adobe Express, enabling component reuse across multiple platforms and significantly reducing development time for new features.
\item Built \textbf{authoring framework} with user entitlement system to control feature access and implement monetization strategies including paywalls and upgrade prompts.
\item Engineered \textbf{"Open Express As You Left"} feature to preserve editor state, directly increasing exports by \textbf{3 million per quarter} by resuming user sessions seamlessly.
\item Created \textbf{Recents \& Suggestions} system for easy access to recently used assets (templates, images, videos) and integrated ML model for intelligent asset recommendations based on user history.
\item Currently developing \textbf{preview generation system} with multiple strategies to create off-screen document snapshots, allowing users to preview feature applications without disrupting their workflow.
\end{tightemize}
\sectionsep

\runsubsection{Nagarro}
\descript{| Software Engineer }
\location{Jan 2021 – June 2022 | Gurgaon, India}
\begin{tightemize}
\item Developed and enhanced \textbf{15+ microservices} using Java, Spring Boot, Spring Data JPA, and PostgreSQL for e-commerce platform supporting millions of users.
\item Built \textbf{coupon microservice} for automated daily and monthly coupon generation, improving customer engagement and retention rates.
\item Implemented \textbf{address validation microservice} providing intelligent address suggestions to users, enhancing user experience and data quality.
\item Actively participated in code reviews and debugging to improve application performance and maintain high code quality standards.
\item Collaborated in continuous improvement initiatives, contributing suggestions and problem-solving solutions to enhance team productivity.
\item \textbf{Promoted from Trainee to Software Engineer} after demonstrating strong technical skills and building 8+ training projects from scratch.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
JavaScript \textbullet{} TypeScript \textbullet{} Java \\
C++ \textbullet{} HTML \textbullet{} CSS \\

\subsection{Frameworks \& Libraries}
React \textbullet{} Redux \textbullet{} Vue.js \\
Next.js \textbullet{} MobX \textbullet{} Lit Web Components \\
Spring Boot \textbullet{} TailwindCSS \\

\subsection{Databases}
SQL \textbullet{} MySQL \textbullet{} PostgreSQL \textbullet{} MongoDB \\

\subsection{Architecture \& APIs}
Microservices \textbullet{} RESTful APIs \\
Data Structures \textbullet{} Algorithms \\
Design Patterns \textbullet{} System Design \\

\subsection{Tools \& IDE}
Git \textbullet{} GitHub \textbullet{} GitLab \textbullet{} JIRA \\
VS Code \textbullet{} IntelliJ IDEA \textbullet{} Postman \\

\subsection{Soft Skills \& Domain}
OOP \textbullet{} Problem-Solving \textbullet{} Leadership \\
Creative Editing Software \textbullet{} E-commerce \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Punjab Technical \newline University}
\descript{Bachelor of Technology in Computer Science and Engineering}
\location{June 2021 | Punjab, India}
\location{CGPA: 8.2/10.0 (Distinction)}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS & ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
\textbf{Competitive Programming}: Ranked \textbf{49th/22,000} and \textbf{463rd/200,000+} in major coding competitions \\
\textbf{Four Star Coder} at CodeChef with 1000+ problems solved across platforms \\
\textbf{Knight Badge} (2nd highest) on LeetCode with max rating 2000+ \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/sudo-sanjeev}{\bf sudo-sanjeev} \\
Medium://  \href{https://medium.com/@sanjeev-singh}{\bf @sanjeev-singh} \\
LeetCode://  \href{https://leetcode.com/u/Sanjeev1709912/}{\bf Sanjeev1709912}
\sectionsep

\end{minipage}
\end{document}
